Fusing Filters with Integer Linear Programming

### 2014-05-16 2014betterfusionforfilters/section/03-SizeInference.tex

For example, the final environment and constraints generated for the @normalize2@ example from Section~\ref{s:Introduction} are as follows:
$$
\begin{array}{ll}
       & x : k_{xs},~ gts : k_{gts},~ \exists k_1,~ k_2,~ k_3 
\\
\vdash & \true 
        ~\wedge~  k_{gts} = k_1
        ~\wedge~  \true
\\     &~~~~~~~~ 
          \wedge~  k_{xs}  ~= k_2
        ~ \wedge~  k_{ys1}  = k_2 
        ~ \wedge~  k_{xs}   = k_3
        ~ \wedge~  k_{ys2}  = k_3
\end{array}
$$

@@

%\textbf{Lemma: sole transducers}.
\TODO{Double check: is this really a sufficient property, or only necessary?}
\textbf{Definition: valid constraints}.
The constraints of a function $f$ are \emph{valid}, if and only if each name $n$ in its bindings will have at most one transducer:
\[
\forall f, \sigma, n.\ f :_s \sigma \implies |trans(binds(f), n)| \le 1
\]
% \textbf{Proof:} by induction on $bs$. If $n = @map@_n~f~ns$,
% then $trans(bs,n) = \bigcup_{x \in ns} trans(bs,x)$.
% As @map@ requires its arguments to have the same size, and @filter@ introduces a fresh size for its output,
% if any of the $trans(bs,x)$ are non-empty, they will refer to the same @filter@.
% The other cases are trivial.

@@

These two properties are used in the integer linear programming formulation, when constructing the program.
When fusing two nodes of different iteration size, at most one pair of parents will need to be checked.

>>>>

For example, the final environment and constraints generated for the @normalize2@ example from Section~\ref{s:Introduction} are as follows:
$$
\begin{array}{ll}
       & x : k_{xs},~ gts : k_{gts},~ \exists k_1,~ k_2,~ k_3 
\\
\vdash & \true 
        ~\wedge~  k_{gts} = k_1
        ~\wedge~  \true
\\     &~~~~~~~~ 
          \wedge~  k_{xs}  ~= k_2
        ~ \wedge~  k_{ys1}  = k_2 
        ~ \wedge~  k_{xs}   = k_3
        ~ \wedge~  k_{ys2}  = k_3
\end{array}
$$
Rule~(SFun) also characterises the functions we accept: A function is \emph{valid} if and only if $\exists \sigma. \SizeF{\function}{\sigma}$.

@@

\textbf{Lemma: sole transducers}.
If a function $f$ is \emph{valid}, then its bindings will have at most one transducer:
\[
\forall f, \sigma, n.\ f :_s \sigma \implies |trans(binds(f), n)| \le 1
\]
% \textbf{Proof:} by induction on $bs$. If $n = @map@_n~f~ns$,
% then $trans(bs,n) = \bigcup_{x \in ns} trans(bs,x)$.
% As @map@ requires its arguments to have the same size, and @filter@ introduces a fresh size for its output,
% if any of the $trans(bs,x)$ are non-empty, they will refer to the same @filter@.
% The other cases are trivial.

@@

These two lemmas are used in the integer linear programming formulation, when constructing the program.
When fusing two nodes of different iteration size, at most one pair of parents will need to be checked.
